Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming

### 2016-08-29 RIP-MISDP-Paper/IEEE_RIP-MISDP_peerreview.tex
PAPER: Changed formulation to no longer impy that d'Aspremont was motivated by newer paper

This motivated d'Aspremont et al.~\cite{Asp08,Asp07} to propose several
relaxations based on semidefinite programming (SDP) to compute upper bounds on the restricted isometry
constants; small upper bounds suffice to guarantee
$\ell_0$-$\ell_1$-equivalence between~\eqref{l0min} and~\eqref{l1min}, but
there exist cases in which the bounds are too weak to give a guarantee.

>>>>

D'Aspremont et al.~\cite{Asp08,Asp07} proposed several
relaxations based on semidefinite programming (SDP) to compute upper bounds on the restricted isometry
constants; small upper bounds suffice to guarantee
$\ell_0$-$\ell_1$-equivalence between~\eqref{l0min} and~\eqref{l1min}, but
there exist cases in which the bounds are too weak to give a guarantee.
